### 2024-10-03 paper/supplementary.tex
added in supplementary for learning first half second half

\newpage
\noindent\boldblue{\large{Supplementary B: Optimal Models}}
\vspace{-1mm}

@@

\noindent Here we define the parameters used for the three models. Note that not all the parameters are used in each model, which we specify further below and in \boldblue{Fig. 2}. The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement. Neuromechanical Delay is the mean ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) of the time between a volitional decision to move and movement onset. Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target. Stimulus Movement onset is knowledge of the mean ($\mu_{S}$) and uncertainty ($\sigma_{S}$) of the stimulus’s movement onset distribution. Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended transition time, $\tau$. Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing. All probability distributions are assumed to be normally distributed with a mean $\mu$ and standard deviation $\sigma$.  Each of our three models has a different set of known and unknown parameters. A model decision policy has full knowledge of known parameters when determining the optimal decision time. A model decision policy has no or partial knowledge of unknown parameters when determining the optimal decision time.

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary C: Model Results}}

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary D: Response Time Task}}

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary E: Timing Uncertainty Task}}

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary F: Guess Decisions}}

>>>>

\newpage
\noindent\boldblue{\large{Supplementary B: First Half and Second Half Data Trends}}
\vspace{-1mm}

\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/exp1_data_panel_first_half.png}
    \caption*{
        \boldblue{Supplementary Figure 3: Outcome Metrics for First Half of Trials}. \boldblue{A)} Indecisions (\%) \boldblue{B)} Wins (\%), and \boldblue{C)} Incorrects (\%) for the first half of trials for each condition. 
        Here we show that analyzing only the first half of trials in each condition displays the same significant differences as the analysis done on all of the trials.         
        This result indicates that participants determined their timing strategy early on in each condition there was a negligible effect of learning on participant's strategies throughout the experiment. 
    } 
\end{figure}

\begin{figure}[H]
\begin{minipage}[c]{0.6\textwidth}
    \includegraphics[scale = 1]{figures/exp1_data_panel_second_half.png}
\end{minipage}\hfill
\begin{minipage}[c]{0.3\textwidth}
    \caption*{
        \boldblue{Supplementary Figure 3: Outcome Metrics for Second Half of Trials} Blah. 
    } 
\end{minipage}
\end{figure}

\newpage
\noindent\boldblue{\large{Supplementary C: Optimal Models}}
\vspace{-1mm}

@@

\noindent Here we define the parameters used for the three models. Note that not all the parameters are used in each model, which we specify further below and in \boldblue{Fig. 2}. The Response Time parameters has both a mean ($\mu_{rt}$) and uncertainty ($\sigma_{rt}$) that represents the delay between observing the stimulus movement onset to initiating a movement. Neuromechanical Delay is the mean ($\mu_{nmd}$) and uncertainty ($\sigma_{nmd}$) of the time between a volitional decision to move and movement onset. Movement Time represents the mean ($\mu_{mt}$) and uncertainty ($\sigma_{mt}$) of the delay between movement onset and reaching a target. Stimulus Movement onset is knowledge of the mean ($\mu_{S}$) and uncertainty ($\sigma_{S}$) of the stimulus’s movement onset distribution. Timing uncertainty ($\sigma_{\tau}$) is the participant uncertainty around the intended transition time, $\tau$. Switch Time represents the additional delay ($\mu_{switch}$) and uncertainty  ($\sigma_{switch}$) of switching from reacting to guessing. All probability distributions are assumed to be normally distributed with a mean $\mu$ and standard deviation $\sigma$.  Each of our three models has a different set of known and unknown parameters. A model decision policy has full knowledge of known parameters, and no or partial knowledge of unknown parameters when determining the optimal decision time.

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary D: Model Results}}

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary E: Response Time Task}}

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary F: Timing Uncertainty Task}}

@@

\newpage
\noindent\boldblue{\large\textcolor{mydarkblue}{Supplementary G: Guess Decisions}}
